\documentclass[../../../patent_v1.tex]{subfiles}

\begin{document}

Automation plays an important role in the world 
economy and in daily experience in the last few 
decades has witnessed a rapid development in audio
systems.

Journey of audio systems begins with single channel 
audio system (monaural audio system) in year 1877, 
later in the year 1931 two channel Audio system 
(Stereo audio system) were introduced and in the year 
2005 the most advanced air audio or surround sound 
system (Multichannel audio system) were introduced.

Modern sound systems are increasingly gaining 
popularity day by day, particularly since technical 
advances have lowered their prices, increased their
qualities and features. One barrier to the greater 
experience while using these sound systems is its 
static nature in case of surround sound. Surround 
sound is a system of stereophony involving three or 
more speakers surrounding the listener so as to give a 
more realistic effect.

Even though high end audio systems provide good quality 
of sound but to achieve the surround sound effect the 
user has to configure the system manually depending 
upon his current position which is a very Tedious task.
Whenever you are settling up your complex home theatre 
bundle, understanding the art and science of speaker 
channel and placement is the most critical step in enjoying 
your new sound system.

Current sound system needs manual setup according to the 
ideal sitting position to achieve a good sound effect at 
fixed position. This manual setup consists of speaker angles 
and speaker sound adjusted to create and sound pocket around 
fixed position. But this effect varies when we move away
from the surround sound pocket created by speakers.

The aim of this project is to develop a real time system to 
determine the listener’s position and distance from the speaker 
system. The real time system described here is based on 
ultrasonic sensors mounted onto servo motors controlled by 
separate micro controllers (slave). The core of the system
is a master micro-controller termed as an audio processing 
unit which controls the speaker direction as well as sound levels. 
Distance measured from the rotating ultrasonic system, allows us 
to map 2 dimensional maps of the room in real time. With less 
system requirements, the surround sound pocket can be
adjusted according to the listener's position.

\end{document}